Detecting Spam on Social Networking Sites

### 2012-05-08 docs/paper/paper.tex
update

To choose a sample of relevant features, we computed statistics on the extracted features, both on the ham and spam corpora. These statistics were generated using SQL on a table created from the merged and cleaned data generated in the process described above.

@@

\textbf{Sender Age:} Spam user age tended to be higher

\textbf{Sender Birthday:} We analyzed

We also noticed that Afghanistan and Albania featured prominently at the 11th and 15th most popular countries f......

@@

\textbf{Sender Photos:} We found that the number of photos that user has uploaded is also indicative of their spam or ham reputation. Spammers

@@

\begin{tabular}{c|c

>>>>

To choose a sample of relevant features, we computed statistics and generated histograms on 
the extracted features, comparing the ham and spam corpora. These statistics were generated 
using SQL on a table created from the merged and cleaned data generated in the process described above.

@@

\textbf{Sender \& Recipient Age:} The age indicated on their profile tended be higher for spam user than 
for ham users, with median ages of 31 and 22 respectively (Figure \ref{fig:sendage}). Likewise, the 
age of message recipients was higher for spam recipients that for recipients of ham messages, with 
median ages of 41 and 22 (Figure \ref{fig:recipage}). The sample size for spam recipient age 
was only 11,000 messages due to late data collection. We posit that the higher ages indicated on spam profiles, 
mirrored in recipient ages, reflects targeting of older users who are more likely to be financially 
stable.

\textbf{Sender Birthday:} We analyzed the birthdays and birth months of ham and spam users and noticed that spam users 
were more likely to have birthdays early in the month, and birth months early in the year. This is illustrated in 
Figures \ref{fig:day} and \ref{fig:month}. Given the drop-down select menus on the web site's registration form, reproduced 
Figure \ref{cite:drop}, it seems likely that this is due to an unwillingness on the part of spam users to 
scroll down to lower options (as well as, perhaps, a hesitance to disclose real birthdates). A similar trend is 
observed in the countries with the most discrepancies between IP-detected countries and countries stated on spam 
user profiles, with Afghanistan and Albania comprising 19\%, despite their relatively low representation on the 
site.

@@

\textbf{Extra Profile Features:} We found that the number of photos that user has uploaded is also indicative of their spam or ham reputation. Spammers

@@
